### 2015-04-17 src/intro/intro.tex
Revert "Fixed page numbers. Minor updates."
This reverts commit 2f63721d72acb4db7c5102088d9b83737ac687b3.
Revert "Revert "Fixed page numbers. Minor updates.""
This reverts commit 3578f0168d31f0be161f95a7c3e13d3fe9932296.

\chapter{General introduction}
\newpage

@@

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/intro/figures/optic_flow.eps}

@@

Similar retinal shifts are also observed during movement of the eyes or head. When interpreting optic flow the brain needs to distinguish object- from self-motion, this process is called optic flow parsing. One strategy is to use extra-retinal cues such as the vestibular, and somatosensory signals to subtract out the retinal stimulation due to self-motion \cite{wertheim1994,wexler2001,macneilage2012}.

@@

A powerful tool in psychophysical research is the two-alternative forced choice (2AFC) paradigm. In this paradigm, participants are presented with two stimuli, e.g. two translation distances, and are then forced to make a choice, e.g. on which of the two translations was longer. By systematically varying one of the choice alternatives (i.e., the probe stimulus), the point of subjective equality, or PSE, can be determined. The PSE is the point at which the participant is completely unsure about which stimulus to pick, i.e. gives a random response, because he perceives the two stimuli as being equal. If the PSE does not line up with the actual reference stimulus, there is a bias in the percept, represented by the Greek letter mu ($\mu$).

@@

Most participants are able to do this perfectly, regardless of the reference angle (see \panelref{intro:fig4}{B}). Their uncertainty has been shown to increase as a function of reference angle though (see \panelref{intro:fig4}{C}).

As the SBT probes body orientation, the somatosensory signal originating from the torso can be used without any reference transformation and thus provides a direct contribution. Other sensory signals such as the vestibular signal can also be used, but only after a reference frame transformation.

@@

When seated straight this task, participants do not make any static errors and are very certain about their responses (see \panelref{intro:fig5}{B} and \hyperref[intro:fig5]{C}). This changes when tilting the participant before the task. In general, the static error increases with tilt angle. When the direction of the error is in the direction of the body mid-line, this effect is known as the Aubert or A-effect \cite{aubert1861}. At smaller angles overcompensation occurs and the static error is in the opposite direction, which is away from the body mid-line. This latter effect is known as the E-effect and could be due to the effects of ocular counter-roll (OCR).

>>>>

\chapter{General introduction}
\chaptermark{}

\newpage

@@

\begin{figure}
    \includegraphics[width=1.0\textwidth]{src/intro/figures/optic_flow.pdf}

@@

Similar retinal shifts are also observed during movement of the eyes or head. When interpreting optic flow the brain needs to distinguish object- from self-motion; this process is called optic flow parsing. One strategy is to use extra-retinal cues such as the vestibular and somatosensory signals to subtract out the retinal stimulation due to self-motion \cite{wertheim1994,wexler2001,macneilage2012}.

@@

A powerful tool in psychophysical research is the two-alternative forced choice (2AFC) paradigm. In this paradigm, participants are presented with two stimuli, e.g. two translation distances, and are then forced to make a choice, e.g. on which of the two translations was longer. By systematically varying one of the choice alternatives (i.e., the probe stimulus), the point of subjective equality, or PSE, can be determined. The PSE is the point at which the participant is completely unsure about which stimulus to pick, i.e. gives a random response, because the participant perceives the two stimuli as being equal. If the PSE does not line up with the actual reference stimulus, there is a bias in the percept, represented by the Greek letter mu ($\mu$).

@@

Most participants are able to do this accurately, regardless of the reference angle (see \panelref{intro:fig4}{B}). Their uncertainty has been shown to increase as a function of reference angle though (see \panelref{intro:fig4}{C}).

As the SBT probes body orientation, the somatosensory signal originating from the torso can be used without any reference transformation and thus provides a direct contribution. Other sensory signals such as the vestibular signal can also be used, but only after a reference frame transformation. We exploit this notion in \Chapter{p1}.

@@

When seated straight this task, participants do not make any static errors and are very certain about their responses (see \panelref{intro:fig5}{B} and \hyperref[intro:fig5]{C}). This changes when tilting the participant before the task. In general, the static error increases with tilt angle. When the direction of the error is in the direction of the body mid-line, this effect is known as the Aubert or A-effect \cite{aubert1861}. At smaller angles overcompensation occurs and the static error is in the opposite direction, which is away from the body mid-line. This latter effect is known as the E-effect and could be due to the effects of ocular counter-roll (OCR). We use this task in \Chapter{p1}.
